---
title: "Test Technik Buying"
subtitle: "Test Plazierung von Produkten"
author: "Benjamin Kampka"
output:
 html_document:
  css: style.css 
  fig_height: 4
  fig_width: 6
  highlight: tango
  number_sections: yes
  theme: paper
  toc: yes
  toc_depth: 3
  toc_float: 
    collapsed: false
    smooth_scroll: true 
  df_print: paged
bibliography: lit.bib
csl: apa.csl
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE, 
	fig.align = 'center'
)
library(tidyverse)
library(knitr)
```


# Beispielhafter Warenkorb:

```{r}
# create a list of baskets
market_basket <-  
  list(  
c("MacBook", "MacBook-Ladekabel", "Ipad", "Iphone"),
c("MacBook", "Macbook-Ladekabel", "Apple-Pencil"),
c("MacBook", "Macbook-Ladekabel"), 
c("Ipad", "Apple-Pencil"),
c("Ipad", "Apple-Pencil", "Iphone"),
c("Ipad", "Apple-Pencil", "MacBook"),
c("MacBook", "Samsung-S20", "Samsung Pencil"),
c("HP-Netbook", "ACDC-Ladekabel", "Samsung-Pencil", "Samsung-S20"), 
c("HP-Netbook", "ACDC-Ladekabel", "Samsung-S20"), 
c("HP-Netbook", "Samsung-S20"),
c("HP-Netbook", "Iphone", "Ipad")
  )

# set transaction names (T1 to T8)
names(market_basket) <- paste("T", c(1:11), sep = "")
```

 We use the measures support, confidence and lift to reduce the number of relationships we need to analyze:

<div class = "blue">

* **Support** is an indication of how frequently a set of items appear in baskets. 
* **Confidence** is an indication of how often the support-rule has been found to be true.
* **Lift** is a measure of association using both support and confidence.

</div>

# Implementation Algorithmus

```{r}
library(arules)
```
## Transform the Data + Summary
```{r}
trans <- as(market_basket, "transactions")
summary(trans)
```

The `summary()` gives us information about our transaction object:

* There are 11 transactions (rows) and 11 items (columns) and we can view the most frequent items.

* Density tells us the percentage of non-zero cells in this 11x11-matrix. 

* Element length distribution: a set of 2 items in 3 transactions; 3 items in 6 of the transactions and 4 items in 2 transactions.

**Das Ganze kann man sich noch in 2 Plots/ Images anschauen**

```{r}
image(trans)
itemFrequencyPlot(trans, topN=10,  cex.names=1)
```

# A-Priori Algorithm

```{r}
rules <- apriori(trans, parameter = list(supp=0.1, conf=0.5, 
                                         maxlen=2, 
                                         minlen=2,
                                         target= "rules"))

```
```{r}
inspect(rules)
```
**It is possible to analyze what items customers buy after buying {Iphone}**
```{r}
mac_rules_lhs <- apriori(trans, 
                          parameter = list(supp=0.1, conf=0.6, 
                                         maxlen=2, 
                                         minlen=2),
                          appearance = list(lhs="Iphone", default="rhs"))
```
Ergebnis:

```{r}
inspect(mac_rules_lhs)
```

## Graphicbasierte Visualisierung

```{r}
library(arulesViz)
subrules <- head(rules, n = 10, by = "confidence")

plot(subrules, method = "graph",  engine = "htmlwidget")
```

## Parralel Coordinate Plot

```{r}
plot(subrules, method="paracoord")
```




